---
title: "Prediction Assignment Writeup"
author: "suwei"
date: "2018-1-9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, message = FALSE)
```
### Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).


### Data

The training data for this project are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.


### Library

Using caret package to analysis. if the package isn't in your environment, it will automatically Install it.

```{r}
libs <- c("caret")
for (i in libs){
  if( !is.element(i, .packages(all.available = TRUE)) ) {
    install.packages(i)
  }
  library(i,character.only = TRUE)
}

sessionInfo()
```

### Data loading and checking

Get the data into r environment.

```{r}
# Data loading
training <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
testing <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")

# Na and no value column counting
naCount <- sapply(1:ncol(training), function(x){sum(is.na(training[ ,x]))+sum(training[, x] == "")})

# Getting new data frame
new_training <- data.frame(training[, which(naCount == 0)])
new_testing <- data.frame(testing[, which(naCount == 0)])

# Remove those columns which are not quiet useful in prediction
new_training <- new_training[, 8:ncol(new_training)]
new_testing <- new_testing[, 8:ncol(new_testing)]
```

### Data Partitioning

First, we can split the original training data in two part. 70% for training and 30% for testing.

```{r}
set.seed(1)
inTrain <- createDataPartition(new_training$classe, p=0.70, list=F)
trainData <- new_training[inTrain, ]
testData <- new_training[-inTrain, ]
```

### Model building

Apply random forest on the training set and use 10 fold cross validation.

```{r}
setting <- trainControl(method="cv", 10)
modelRandomForest <- train(classe ~ ., data = trainData, method = "rf", trControl = setting)
modelRandomForest
```

### Predicting

We can use the model to predict the data in `testData` which was splited from the original `train` dataset.

```{r}
predict <- predict(modelRandomForest, testData)
result <- confusionMatrix(testData$classe, predict)
result
```

From the model, we can know the accuracy is `r result$overall[[1]]*100` % and the error is `r (1-result$overall[[1]])*100`%.

Next, we use the model to predict data which isn't knowing the classes.

```{r}
predictTest <- predict(modelRandomForest, new_testing)
predictTest
```